ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-05-06 paper.tex
We did it!!

There are an estimated half a billion people that live with mild to severe vision impairment or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}.
There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
The work we present here is part of the ActiVis project that aims to assist people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
This project expands upon concepts proposed in~\cite{bellotto2013,lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.

@@

ActiVis uses the camera's current and previous image data as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to take to reach the target object.
To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP) on a mobile phone that generates real-time navigation instructions to guide the user to their target object.
This work makes the following contributions:

@@

Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and controller in Section~\ref{sec:active-vision}.
The experiments and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.

@@

%Mobile devices that can detect objects and guide PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing and image processing methods.
Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}. 
The device uses a feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors have made it viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects while providing the same guidance functionality.
%The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.
An alternative detection approach proposed in~\cite{bigham2010vizwiz} requires the user to send a photo of their environment to a Mechanical Turk worker that sends the position of the requested object within the picture back to the user.

The issue with a marker-based approach is that it requires significant effort to place and maintain them in an environment, which is remedied by markerless systems.
However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves before any guidance is provided. 
The system in~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to help guide a user to the correct location, but the there is significant lag and a reliance on a good internet connection and remote worker being available. 
Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that provides the user with pointing instructions to find an out-of-view object and proved that this is a viable method to search for an object. 
However, this work used barcodes encoded with object information to simulate real objects.
In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.

@@

The ActiVis project's goal is developing a mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
%This work focuses on guiding a user towards an object in one static environment and is limited to 2 dimensions (pan and tilt).

A complete system diagram is given in Fig.~\ref{fig:sys-diagram}. 
This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, but has been modified to incorporate a human within the loop.

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figures/control_loop.png}
  \caption{The system control loop including a human and the controller.}\label{fig:sys-diagram}
\end{figure}

%The error, $e$, is defined as the difference between the desired object and the object currently within view. 
Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge is that a person may interpret \emph{u} in any unpredictable way that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
The object detector's classification errors, \emph{n}, is added to the feedback loop as a noise signal and affects \emph{K}'s output.

In our previous work~cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and extend the MDP and implement a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers. 
%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
This controller works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
The design and implementation of this controller are discussed next.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\columnwidth]{figures/desk_example.png}
  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects}\label{fig:openimage}
\end{figure}

@@

\begin{table}[h]
  \centering
  \caption{The reward function for the POMDP. }\label{tab:rewards}
  \begin{tabular}{p{3cm}p{1cm}}
    \toprule
    $r(o = o_{target})$ & 10000 \\ \midrule
    $r(v = \textrm{true})$  & -75 \\ \midrule
    $r(n > n_{\max})$ & -75 \\ \midrule
    otherwise $r(\cdot)$ & -100  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

The POMDP model is put through a training process to generate a policy that contains the optimal belief-action mapping that the controller can use to produce the optimal waypoint locations.
This is done by having the model explore the entire state-action-observation space and optimising the policy to maximise its long-term cumulative reward.
The difficulty of solving POMDPs is that $\mathbf{b}$ is a vector of continuous probability distributions with infinite combinations, making POMDPs time-consuming or even impossible to solve exactly.
We found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
In this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library\footnote{github.com/Svalorzen/AI-Toolbox} to solve the POMDP model.
The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking these points only. 
Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.

@@

We implemented the object detector and POMDP controller by combining it with an audio interface that provides non-visual guidance instructions onto an Android app.% that can be used by a PwVI by adding .% onto a mobile phone that can generate and provide guidance instructions for a user.  
Non-visual feedback allows the app to be used by PwVI.
%This was done by combining an audio interface that provides non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
Each of these aspects and their implementation are discussed here.

\subsubsection{Audio Interface}

ActiVis's target audience are PwVI and therefore provides guidance instructions in a non-visual manner that is intuitive and easy to understand. 
To avoid blocking a user's access to ambient sounds, we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.

To describe the waypoints' pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
However, since our headphones bypass the ear's pinnae that allow a person to localise the height~\cite{roffler1968factors}, we spatialise the audio in the pan dimension only.
To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch accordingly. 
%A similar approach was used in~\cite{schauerte2012assistive}.
With this interface and headset, ActiVis is able to describe location of a waypoint to a user in the pan and tilt dimensions.

\subsubsection{Object Detector}

SSD-Lite is a single-stage object detection and classification network that is based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.%~\cite{lin2014microsoft}. 
The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
%Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.

The network was trained with a maximum of 10000 object samples, taken from the OpenImages dataset~\cite{openimages}, for each object class in $\mathbf{U}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
With 120 training epochs with 1000 iterations each, we achieved a mAPs of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android. 
%We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
%This dataset contains 459 images for each of the objects in $\mathbf{U}$ in different sizes and orientations and the objects used were the same objects that were used in the experiments. 
%\todo{add mAPs we achived}

\subsubsection{Action Generator}

The output from the POMDP model's training process is a policy file that defines the best location to place the next search waypoint based on the device's current state.
This state is tracked by the device throughout the app's runtime by performing object detection and recording the device's previous search locations and previous waypoint positions
The latter is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
Each grid square represents a \SI{35}{\degree} angular translation and the grid encompasses a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
This setup gives the state access to perfectly observable $n$ and $v$ parameters, while $o$ is generated by the object detector.

When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
The controller uses $\omega$ to update $\mathbf{b}$ and queries the policy for the best location to place the new waypoint. 
The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.\ `UP' output would result in a waypoint being placed one grid square above the grid square within view.

@@

Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement. 
However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences which is not a problem since most offices contain the same basic furniture and objects. 
The objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects between experiments. 
The objects in the guided experiment environment are

\begin{equation*}
  \mathbf{u}_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
\end{equation*}
while the objects in the unguided experiment are

\begin{equation*}
  \mathbf{u}_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
\end{equation*}

We recruited 10 participants (8 male, 2 female; average age 29.2 years) for the experiments, including 2 legally blind participants. 
The other 8 participants were blindfolded to simulate blindness. 
The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{developers.google.com/ar/} and text-to-speech enabled.

@@

For this experiment, the mobile camera and object detector acts as the participants' eyes and informs them about the objects within the camera's view.
It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller} where the human acts as both the actuator and controller.
The app only reads out the objects upon the user's request by tapping on the screen. 
When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/control_loop_no_controller.png}
  \caption{The control loop with the human acting as bot manipulator and controller. }\label{fig:sys-diagram-no-controller}
\end{figure}

Each participant was verbally informed prior to each experiment what the target object was and they were given 45 seconds to find it and each run was ended when a target was found or the time limit was reached. 
The learning effect was ignored in order to mimic the normal search behaviour described earlier and allow full use of prior knowledge. 
This process performed once for each object in the experiment set.

@@

The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object faster themselves.
This also isolated the performance measurement to the guidance system alone.
An experiment run started with the experiment staff selecting the target and was terminated when the target object was found or the 45 second time limit was reached.
This process performed once for each object in the experiment set.

@@

The target acquisition rate (TAR) is the proportion of objects the participants successfully found during an experiment. 
For example, a TAR of 0.5 indicates that a participant found the target object in 50\% of searches. 
Taking each participant's TAR as a datum, we found the unguided case produced a higher average TAR (0.54 vs. 0.46), meaning that a participant found around 8\% more objects without guidance instructions.
However, the Kruskal-Wallis (KW) test for non-normal data shows that these results are statistically not significantly different from one another ($p_{kw} = 0.16$), meaning we cannot conclude which experiment produced the best TAR. 
All the experiment results are summarised in Table~\ref{tab:results}.

@@

The device displacement was measured in both linear ($x, y, z$) and angular (pan, tilt) dimensions.
By integrating these data we obtain and compare the total absolute displacement in each dimension.
These results are plotted in Fig.~\ref{fig:boxplot-displacement}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}
\end{figure}

>>>>

There are an estimated half a billion people that live with mild to severe vision impairment or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}.
There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
This work is part of the ActiVis project that aims to enable people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
This project expands upon concepts proposed in~\cite{bellotto2013,lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.

@@

ActiVis uses the camera's current and previous image data as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to take to find the target object.
For this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP) on a mobile phone that generates real-time navigation instructions for the user.
This work makes the following contributions:

@@

Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and controller in Section~\ref{sec:active-vision}.
The experiments and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}.
The paper is concluded in Section~\ref{sec:conclusion}.

@@

%Mobile devices that can detect objects and guide PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing and image processing methods.
Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}. 
The device uses audio feedback to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors have made it viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture. 
%that requires the user to send a photo of their environment to a Mechanical Turk worker who sends the position of the requested object within the picture back to the user. 
%The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.

The issue with a marker-based approach is that it requires significant effort to place and maintain them in an environment, which is remedied by markerless systems.
However, both of these methods use passive guidance approaches that rely on the user placing the desired marker/object within the camera's view by themselves before any guidance is provided. 
VizWiz~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to guide a user to the correct location, but the there is significant lag and a reliance on a good internet connection and remote worker being available. 
Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that gives the user pointing instructions to find an out-of-view object and showed that this is a viable method of object search. 
However, this work used encoded barcodes to simulate real objects.
In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.

@@

%The ActiVis project's goal is developing a mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
%This work focuses on guiding a user towards an object in one static environment and is limited to 2 dimensions (pan and tilt).

A complete system diagram for Activis is given in Fig.~\ref{fig:sys-diagram}. 
This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, but has been modified to incorporate a human within the loop.

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/control_loop.png}
  \caption{The system control loop including a human and the controller.}\label{fig:sys-diagram}
\end{figure}

%The error, $e$, is defined as the difference between the desired object and the object currently within view. 
Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives a control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge is that a person may interpret \emph{u} in any unpredictable way that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
The object detector's classification errors, \emph{n}, is added to the feedback loop as a noise signal and affects \emph{K}'s output.

In our previous work~\cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and extend the MDP and implement a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers. 
%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
This controller works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
The design and implementation of this controller are discussed next.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\columnwidth]{figures/desk_example.png}
  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects}\label{fig:openimage}
\end{figure}

@@

\begin{table}
  \centering
  \caption{The reward function for the POMDP. }\label{tab:rewards}
  \begin{tabular}{p{3cm}p{1cm}}
    \toprule
    $r(o = o_{target})$ & 10000 \\ \midrule
    $r(v = \textrm{true})$  & -75 \\ \midrule
    $r(n > n_{\max})$ & -75 \\ \midrule
    otherwise $r(\cdot)$ & -100  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

The POMDP model is put through a training process to generate a policy that contains the optimal belief-action mapping that the controller can use to produce the optimal waypoint locations.
This is done by having the model explore the entire state-action-observation space and optimising the policy to maximise its long-term cumulative reward.
However, $\mathbf{b}$ is a vector of continuous probability distributions with infinite combinations, making POMDPs time-consuming or even impossible to solve exactly.
We found this to be the case for our moderately-sized state space size and opted for an approximate method instead.
We used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point}, as implemented in the AI-Toolbox library\footnote{github.com/Svalorzen/AI-Toolbox}, to solve the POMDP model.
The PBVI algorithm speeds up the training process by selecting a smaller subset of representative belief points from $\mathbf{b}$ and tracking these points only. 
Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.

@@

%Non-visual feedback allows the app to be used by PwVI.
%This was done by combining an audio interface that provides non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
%Each of these aspects and their implementation are discussed here.

%\subsubsection{Audio Interface}

We implemented the object detector and POMDP controller into an Android app and combined it with an audio interface that provides non-visual guidance instructions.
% that can be used by a PwVI by adding .% onto a mobile phone that can generate and provide guidance instructions for a user.  
%ActiVis's target audience are PwVI and therefore provides guidance instructions in a non-visual manner that is intuitive and easy to understand. 
To avoid blocking a user's access to ambient sounds, we use non-intrusive bone-conducting headphones to transmit the audio signals to the user.

To describe the waypoints' pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
However, since our headphones bypass the ear's pinnae that allow a person to localise the height~\cite{roffler1968factors}, we spatialise the audio in the pan dimension only.
To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch accordingly. 
A similar approach was used in~\cite{schauerte2012assistive}.
%This interface enables ActiVis to describe the location of a waypoint to a user in the pan and tilt dimensions.

%\subsubsection{Object Detector}

SSD-Lite is a single-stage object detection and classification network that is based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.
The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
%Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.

The network was trained with a maximum of 10000 object samples for each class in $\mathbf{U}$, taken from the OpenImages dataset~\cite{openimages}, with a 60\%/20\%/20\% split for training, validation and testing respectively.
We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
With 120 training epochs with 1000 iterations each, we achieved a mAPs of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android and we used this model to implement an SSD-Lite object detector onto a mobile device.
%We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
%This dataset contains 459 images for each of the objects in $\mathbf{U}$ in different sizes and orientations and the objects used were the same objects that were used in the experiments. 
%\todo{add mAPs we achived}

%\subsubsection{Action Generator}

To generate new waypoints, the system uses the policy file output from the POMDP model's training process that defines the best location to place the next search waypoint based on the device's current state.
This state is tracked by the device throughout the app's runtime by performing object detection and recording the device's previous search locations and previous waypoint positions
The latter is done by disretising the world into a $6\times6$ grid, each representing a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value.
%Each grid square represents a \SI{35}{\degree} angular translation and the grid encompasses a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
This setup gives the state access to perfectly observable $n$ and $v$ parameters, while $o$ is generated by the object detector. 
When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
The controller uses $\omega$ to update $\mathbf{b}$ and queries the policy for the best location to place the new waypoint. 
The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.\ `UP' output would result in a waypoint being placed one grid square above the grid square within view.

@@

Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement, though some cross-experiment occurrences appear with the larger, more static objects. 
%However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences which is not a problem since most offices contain the same basic furniture and objects. 
The objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects between experiments. 
The objects in the guided experiment environment are $\mathbf{u}_{guided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $laptop$, $backpack$, $mug \}$, while the objects in the unguided experiment are $\mathbf{u}_{unguided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $monitor$, $telephone$, $keyboard \}$.

We recruited 10 participants (8 male, 2 female; average age 29.2 years) for the experiments, including 2 legally blind participants. 
The other 8 participants were blindfolded to simulate blindness. 
The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{developers.google.com/ar/} and text-to-speech enabled. 
A time limit of 45 seconds was set for each experiment run, which was ended when the target object was found or the time limit was reached, and there was one experiment run per target in the respective environment.

@@

For this experiment, the mobile camera and object detector acts as the participants' eyes and informs them about the objects within the camera's view.
It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
%This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller} where the human acts as both the actuator and controller.
In this case, the human acts as both the controller and actuator. 
The app only reads out the objects upon the user's request by tapping on the screen. 
When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.

%\begin{figure}
  %\centering
  %\includegraphics[width=0.4\textwidth]{figures/control_loop_no_controller.png}
  %\caption{The control loop with the human acting as both manipulator and controller. }\label{fig:sys-diagram-no-controller}
%\end{figure}

%Each participant was verbally informed prior to each experiment what the target object was.
%The learning effect was ignored in order to mimic the normal search behaviour described earlier and allow full use of prior knowledge. 
%This process performed once for each object in the experiment set.

To mimic the normal search behaviour and allow the participant's to use their intuition and prior knowledge, we ignored the learning effect for this experiment and verbally informed them what their target was for each experiment run.

@@

The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object faster themselves.
This also isolated the performance measurement to the guidance system alone.
An experiment run started with the experiment staff selecting the target.
%and was terminated when the target object was found or the 45 second time limit was reached.
%This process performed once for each object in the experiment set.

@@

The target acquisition rate (TAR) is the proportion of objects the participants found during an experiment. 
For example, a TAR of 0.5 indicates that a participant found the target object in 50\% of searches. 
Taking each participant's TAR as a datum, we found the unguided case produced a higher average TAR (0.54 vs. 0.46), meaning that participants found 8\% more objects without guidance instructions.
However, the Kruskal-Wallis (KW) test for non-normal data shows that these results are statistically not significantly different ($p_{kw} = 0.16$), meaning we cannot conclude which experiment produced the best TAR. 
All the experiment results are summarised in Table~\ref{tab:results}.

@@

The device displacement was measured in both linear ($x, y, z$) and angular (pan, tilt) dimensions.
Integrating these data, we obtain the total absolute displacement in each dimension.
These results are plotted in Fig.~\ref{fig:boxplot-displacement}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_displacement.png}
  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}
\end{figure}
